Model matters with restricted Boltzmann machines

### 2017-02-13 presentations/msu/slides.Rmd
add MSU

---
title: "Model matters with restricted Boltzmann machines"
shorttitle: "Model matters with RBMs"
author: Andee Kaplan
shortname: Kaplan, et al.
institute: |
    | Iowa State University
    | ajkaplan@iastate.edu
shortinstitute: ajkaplan@iastate.edu
date: |
  | February 7, 2017
  |
  | Slides available at <http://bit.ly/kaplan-uiuc>
  | 
  | \footnotesize Joint work with D. Nordman and S. Vardeman
shortdate: "February 7, 2017"
output: 
  beamer_presentation:
    template: latex/beamer.tex
    includes:
      in_header: latex/front-matter.tex
theme: CambridgeUS
bibliography: latex/refs.bib
fig_caption: true
nocite: |
    @salakhutdinov2009deep, @kaiser2007statistical
---

@@

2. two layers of random variables - one hidden and one visible
3. conditional independence within a layer [@smolensky1986information]

@@

* Slides -- <http://bit.ly/kaplan-uiuc>

>>>>

---
title: "Model matters with restricted Boltzmann machines"
shorttitle: "Model matters with RBMs"
author: Andee Kaplan
shortname: Kaplan, et al.
institute: |
    | Iowa State University
    | ajkaplan@iastate.edu
shortinstitute: ajkaplan@iastate.edu
date: |
  | February 7, 2017
  |
  | Slides available at <http://bit.ly/kaplan-msu>
  | 
  | \footnotesize Joint work with D. Nordman and S. Vardeman
shortdate: "February 7, 2017"
output: 
  beamer_presentation:
    template: latex/beamer.tex
    includes:
      in_header: latex/front-matter.tex
theme: CambridgeUS
bibliography: latex/refs.bib
fig_caption: true
nocite: |
    @salakhutdinov2009deep, @kaiser2007statistical
---

@@

1. two layers of random variables - one hidden and one visible
2. conditional independence within a layer [@smolensky1986information]

@@

* Slides -- <http://bit.ly/kaplan-msu>
